\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{mathpazo}

% Color Definitions
\definecolor{brandnavy}{HTML}{06101D}
\definecolor{brandgold}{HTML}{FFD700}
\definecolor{lightgray}{gray}{0.95}

% Section formatting
\titleformat{\section}{\color{brandnavy}\Large\bfseries}{\thesection}{1em}{}[\vspace{0.1ex}\titlerule]
\titleformat{\subsection}{\color{brandnavy!80!black}\large\bfseries}{\thesubsection}{1em}{}

% Code listing style
\lstset{
    backgroundcolor=\color{lightgray},
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    rulecolor=\color{lightgray},
    numbers=none
}

% Document Info
\title{
    \vspace{2cm}
    \textbf{\Huge BCCI Intelligence System}\\
    \vspace{0.5cm}
    \Large Official Technical \& Implementation Documentation
}
\author{Engineering \& Analytics Division}
\date{May 2026}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Introduction}
The BCCI Intelligence System is an enterprise-grade, React-based web dashboard designed exclusively for official stakeholders and executive operators. It provides a real-time analytical deep-dive into franchise valuations, systemic challenges, strategic solutions, and ecosystem sustainability. 

\section{Technical Architecture}
The system is built on a modern, high-performance web stack:
\begin{itemize}[label=\textcolor{brandgold}{\textbullet}]
    \item \textbf{Core Framework:} React.js (v19) configured with Vite for lightning-fast HMR and optimized builds.
    \item \textbf{Styling Engine:} Tailwind CSS v4 utilizing native CSS variable injection and JIT compilation.
    \item \textbf{Animation Engine:} Framer Motion for staggered reveals, layout transitions, and high-fidelity micro-interactions.
    \item \textbf{Data Visualization:} Recharts (Area charts, Bar charts, Pie charts) engineered to render SVG data visualizations securely and dynamically.
    \item \textbf{Routing:} React Router DOM for seamless Single Page Application (SPA) navigation.
    \item \textbf{Iconography:} \texttt{lucide-react} for crisp, scalable, and consistent vector iconography.
\end{itemize}

\section{User Interface \& Design System}
The overall aesthetic leans into an "Executive Glassmorphism" layout. It abandons traditional flat web design in favor of visual layering that implies security, depth, and intelligence.

\subsection{Design Tokens}
\begin{itemize}
    \item \textbf{Brand Navy (\texttt{\#0B192C}, \texttt{\#06101d}):} Used as the core background and structural anchor to simulate an analytical terminal.
    \item \textbf{Brand Gold (\texttt{\#FFD700} to \texttt{\#D4AF37}):} Used selectively for glowing accents, impact scores, active navigational states, and typography highlights.
\end{itemize}

\subsection{Glassmorphism Implementation}
Distinct CSS utility classes (\texttt{.glass-card}, \texttt{.glass-dark}) were implemented using CSS \texttt{backdrop-filter: blur()}, pseudo-elements, and semi-transparent RGBA borders to simulate frosted glass floating above dynamic gradients.

\section{Feature Map \& Modules}

\subsection{Main Executive Dashboard (Home)}
The landing portal features staggered animation reveals of macro statistics (Total Ecosystem Valuation, Broadcast cycles, Global Audience metrics) backed by glowing visual orbs and large-format typography.

\subsection{Deep Analytics Module}
Houses the core Recharts implementations:
\begin{itemize}
    \item \textbf{Valuation Trajectory:} An interactive AreaChart detailing the precise year-on-year growth of average franchise values from \$50M (2008) to over \$1.5B (Present).
    \item \textbf{Match Outcomes:} Ring/Pie charts breaking down historical win conditions.
    \item \textbf{Elite Tier Talent Impact:} A custom-designed dark-mode table ranking top players via an aggregated "Impact Score", utilizing data-grids and glowing CSS badges.
\end{itemize}

\subsection{Strategic Pages (Paradox, Pros/Cons, Challenges, Solutions)}
Each distinct route provides deep business narratives mapped through complex React structural layouts. They address ecosystem imbalances, localized financial dependencies, and actionable resolutions—all rendered interactively.

\subsection{Secure Navigation Sidebar}
A fixed, left-aligned command center featuring active-routing states, glowing indicators, and pulsing operational badges indicating server security and application bounds.

\section{Development Scripts}
\begin{lstlisting}[language=bash, title=Starting the Development Server]
# Install Dependencies
npm install

# Start the Vite Dev Server
npm run dev
\end{lstlisting}

\end{document}